Output Summary

### 2025-05-01 03-post-process/output-plots-children/08-misc-processes.Rmd
Improve misc processes Rmd section
Minor aesthetic/organizational changes to output plots

# Miscellaneous Processes {.tabset .tabset-pills}

@@

## Ocean Survival {.tabset .tabset-pills}

### Yr1 {.tabset .tabset-pills}

#### NOR {.tabset .tabset-pills}

##### Realized Alone

@@

@@

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Yr1 Ocean Survival (NOR)")
```

##### Realized & [Expected + AR(1)]

@@

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Yr1 Ocean Survival (NOR)")
```

#### HOR {.tabset .tabset-pills}

##### Realized Alone

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Yr1 Ocean Survival (HOR)")
```

### Yr2 {.tabset .tabset-pills}

#### NOR

@@

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Yr2 Ocean Survival (NOR)")
```

#### HOR

@@

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Yr2 Ocean Survival (HOR)")
```

### Yr3 {.tabset .tabset-pills}

#### NOR

@@

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Yr3 Ocean Survival (NOR)")
```

#### HOR

@@

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Yr3 Ocean Survival (HOR)")
```

@@

#### NOR

@@

#### HOR

>>>>

# Miscellaneous Processes {.tabset .tabset-dropdown}

@@

## Ocean Survival {.tabset .tabset-dropdown}

### Year-1 {.tabset .tabset-pills}

#### Realized Alone {.tabset .tabset-pills}

@@

##### (a) NOR {-}

@@

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Year-1 Ocean Survival (NOR)")
```

##### (b) HOR {-}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Year-1 Ocean Survival (HOR)")
```

#### Realized & [Expected + AR(1)] {.tabset .tabset-pills}

@@

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Year-1 Ocean Survival (NOR)")
```

### Year-2 {.tabset .tabset-pills}

#### (a) NOR {-}

@@

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Year-2 Ocean Survival (NOR)")
```

#### (b) HOR {-}

@@

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Year-2 Ocean Survival (HOR)")
```

### Year-3 {.tabset .tabset-pills}

#### (a) NOR {-}

@@

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Year-3 Ocean Survival (NOR)")
```

#### (b) HOR {-}

@@

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Year-3 Ocean Survival (HOR)")
```

@@

#### (a) NOR {-}

@@

#### (b) HOR {-}
